---
title: "Who does more pushups"
author: "your name"
date: "March 8"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

My method is to create a box and whiskers plot showing the max pushups of all the skill players on one side and all the line players on the other. That will show us the mean, median, and range of each group.

# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->



## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->

```{r}
boxplot(pushups ~ position,data=pushups)
```

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
t.test(pushups ~ position,data=pushups)
```

# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

You can tell by looking at the box and whisker plot that the difference is almost unbelievable. Were you to bring the two boxes together, they would not touch. That is proof as to how different the two stats are. Usually statisticians consider a Pvalue below .05 to be a definitive no correlation. The TTest above gives us a Pvalue of 0.000009421 meaning the stats have no similarities. The boxplot makes it very clear that the skill players do more pushups than the line players although there are some line players that do more pushups than some skill players.

# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

My conclusion is that skill players on average do more pushups that line players. I imagine this is due to skill players having to be lighter and more agile than line players so that they can outrun their opponents. Line players have to be heavier, larger, and stronger in order to act as a wall keeping their quarterback safe while he decides the play to make.
